Co-moving stars in \textsl{Gaia DR1}:\\ An abundance of very wide separation co-moving pairs

### 2017-02-24 paper/ms.tex
update catalog; other minor tweaks

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{likelihoodratios.pdf}
  \end{center}
  \caption{%
    Justification of the likelihood ratio cut.
    On the top row, we show how the distribution of $\ln \mathcal{L}_1 /\mathcal{L}_2$
    changes (left) in slices of \absdvtan\ (sequentially color-coded in pink on the right panel).
    On the bottom row, we show how the distribution of pairs on \absdvtan\ vs. separation changes (right)
    in slices of $\ln \mathcal{L}_1 /\mathcal{L}_2$ (sequentially color-coded in blue on the left).
    The black dots in the upper right panel and
    the black line in the lower lef panel correspond to the entire initial sample of pairs.
    For comparision, we also present the likelihood ratio distribution of random pairs
    of stars in the \tgas\ with parallax $S/N>8$ in gray filled histogram.
    Based on this, we choose $\ln \mathcal{L}_1 /\mathcal{L}_2 > 6$ as our high-confidence
    candidate co-moving pairs.
    \label{fig:likelihoodratios}}
    \vspace{1em}
\end{figure*}

@@

\subsection{Catalog of candidate co-moving pairs}

In this section, we describe our catalog of candidate co-moving pairs of stars.
For 13,058 pairs (10,606 unique stars) found in this work.
The catalog is composed of three tables of stars, pairs, and groups.
We summarize the content of each table in Table~\ref{tab:table_meta}, and
the relationships between the tables in Figure~\ref{fig:schema}.
The star table contains all 10,606 stars that has at least one co-moving neighbor
by our selection. We provide the TGAS source id, which may be used to easily
retrieve cross matches of \gaia\ with other surveys
using the \gaia\ data archive.
For each star, we also include the positional measurements from \tgas,
\gaia\ $G$-band and \tmass\ $J$, $H$-band magnitudes as well as
\rave\ radial velocities.
The co-moving relationship between the stars is described in the pair table.
We also list the angular and physical separation of pairs, and the likelihood ratio,
$\ln \mathcal{L}_1 /\mathcal{L}_2>6$ (see \eqname~\ref{eq:hyp1} and \ref{eq:hyp2})
computed in this work.

Finally, the information about the connected components found in these co-moving
star graph is in the group table. We assign a unique index to each group
in descending order of its size. Thus, group 0 is the largest group
that contains 151 stars.
Each star or pair is associated with a group that it is a member of, listed
in the group id column of the star and pair table.
Additionally, given the strong correlation between the larger connected 
components of co-moving pairs and the known star clusters,
we provided
%
\begin{itemize}
  \item index and name of the closest cluster in the Milky Way Star Cluster catalog of
  \citet{Kharchenko:2016aa} using 3D separation
  \item distance to the closest cluster in pc
  % \item ID of the OB association (A-L) if the star is in the catalog of
  % stars in the known OB associations by \citet{de-Zeeuw:1999aa}
\end{itemize}

% The distances and physical separations are calculated using the point-estimate
% of distances (\eqname~\ref{eq:dist}).

% \input{stub}
\input{table_meta}

@@

\begin{figure}[htb]
  \centering
  \input{schema.tex}
  \caption{Schematic diagram of the relationship between the tables.}
  \label{fig:schema}
\end{figure}

>>>>

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{likelihoodratios.pdf}
  \end{center}
  \caption{%
    Justification of the likelihood ratio cut.
    On the top row, we show how the distribution of $\ln \mathcal{L}_1 /\mathcal{L}_2$
    changes (left) in slices of \absdvtan\ (sequentially color-coded in pink on the right panel).
    On the bottom row, we show how the distribution of pairs on \absdvtan\ vs. separation changes (right)
    in slices of $\ln \mathcal{L}_1 /\mathcal{L}_2$ (sequentially color-coded in blue on the left).
    The black dots in the upper right panel and
    the black line in the lower left panel correspond to the entire initial sample of pairs.
    For comparison, we also present the likelihood ratio distribution of random pairs
    of stars in the \tgas\ with parallax $S/N>8$ in gray filled histogram.
    Based on this, we choose $\ln \mathcal{L}_1 /\mathcal{L}_2 > 6$ as our high-confidence
    candidate co-moving pairs.
    \label{fig:likelihoodratios}}
    \vspace{1em}
\end{figure*}

@@

\subsection{Catalog of candidate co-moving pairs}
\label{sub:catalog}

\input{table_meta}

\begin{figure}[htbp]
  \centering
  \input{schema.tex}
  \caption{Schematic diagram of the relationship between the tables.
    See \sectionname~\ref{sub:catalog} and Table~\ref{tab:table_meta} for details.
    \label{fig:schema}}
\end{figure}

In this section, we describe our catalog of candidate co-moving pairs of stars.
For 13,058 pairs (10,606 unique stars) found in this work.
The catalog is composed of three tables of stars, pairs, and groups.
We summarize the content of each table in Table~\ref{tab:table_meta}, and
the relationships between the tables in Figure~\ref{fig:schema}.
The star table contains all 10,606 stars that has at least one co-moving neighbor
by our selection. We provide the TGAS source id, which may be used to easily
retrieve cross matches of \gaia\ with other surveys
using the \gaia\ data archive.
For each star, we also include the positional measurements from \tgas,
\gaia\ $G$-band and \tmass\ $J$-band magnitudes as well as
\rave\ radial velocities.
The co-moving relationship between the stars is described in the pair table.
We also list the angular and physical separation of pairs, and the likelihood ratio,
$\ln \mathcal{L}_1 /\mathcal{L}_2>6$ (see \eqname~\ref{eq:hyp1} and \ref{eq:hyp2})
computed in this work.

Finally, the information about the connected components found in these co-moving
star pairs is in the group table. We assign a unique index to each group
in descending order of its size. Thus, group 0 is the largest group
that contains 151 stars.
Each star or pair is associated with a group that it is a member of, listed
in the group id column of the star and pair table.

@@

### 2017-02-24 paper/table_meta.tex
update catalog; other minor tweaks

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column Name    & Unit & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id         &      & zero-based row index                      \\
TGAS source id &      & unique source id from \tgas               \\
RA             & deg  & right ascension from \tgas                \\
DEC            & deg  & declination from \tgas                    \\
parallax       & mas  & unique source id from \tgas               \\
distance       & pc   & unique source id from \tgas               \\
$G$            & mag  & \gaia\ $G$-band magnitudes                \\
$J$            & mag  & \tmass\ $J$-band magnitudes               \\
$H$            & mag  & \tmass\ $H$-band magnitudes               \\
RAVE OBS ID    &      & unique id of the \rave\ match             \\
RV             & \kms & radial velocity from \rave\               \\
eRV            & \kms & uncertainty of radial velocity from \rave \\
group id       &      & Id of the group this star belongs to      \\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
angsep                           & arcmin & angular separation                  \\
separation                       & pc     & physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & likelihood ratio                    \\
group id                         &        & id of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id     &        & unique group id                     \\
size   &        & number of stars in a group          \\
       &        &                                     \\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column Name    & Unit & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id         &      & Zero-based row index                      \\
TGAS source id &      & Unique source id from \tgas               \\
RA             & deg  & Right ascension from \tgas                \\
DEC            & deg  & Declination from \tgas                    \\
parallax       & mas  & Unique source id from \tgas               \\
distance       & pc   & Unique source id from \tgas               \\
$G$            & mag  & \gaia\ $G$-band magnitudes                \\
$J$            & mag  & \tmass\ $J$-band magnitudes               \\
RAVE OBS ID    &      & Unique id of the \rave\ match             \\
RV             & \kms & Radial velocity from \rave\               \\
eRV            & \kms & Uncertainty of radial velocity from \rave \\
group id       &      & Id of the group this star belongs to      \\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
star 1                           &        & Index of star 1 in the star table   \\
star 2                           &        & Index of star 2 in the star table   \\
angsep                           & arcmin & Angular separation                  \\
separation                       & pc     & Physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & Likelihood ratio                    \\
group id                         &        & Id of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id            &        & Unique group id                     \\
size          &        & Number of stars in a group          \\
mean RA       &  deg   & Mean right ascension of members     \\
mean DEC      &  deg   & Mean declination of members     \\
mean distance &  pc    & Mean distance of members     \\
\hline\hline
\end{tabular}
\end{table}
